---
title: "p8105_hw5_zj2379"
author: "Zheshu Jiang"
date: "2023-11-12"
output: github_document
---

## Problem 1
```{r}
library(tidyverse)
# Create a city_state variable
homicide_df = read.csv("./homicide-data.csv")|>
 mutate(city_state = paste(city, state, sep = ", "))

#summarize within cities to obtain the total number of homicides and the number of unsolved homicides 
homicide_df1=homicide_df |>
  group_by (city) |>
  summarize(total_homicides=n(),
            unsolved_homicides=sum(disposition %in% c("Closed without arrest","Closed by arrest")))
homicide_df1
```

For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r}
baltimore_homicides <- homicide_df %>%
  filter(city == "Baltimore", state == "MD")

# Use prop.test to estimate the proportion of unsolved homicides
unsolved_homicides <- sum(baltimore_homicides$disposition %in% c("Closed without arrest", "Open/No arrest"))
total_homicides <- nrow(baltimore_homicides)

prop_test_result <- prop.test(unsolved_homicides, total_homicides)

# Tidy the result of prop.test using broom::tidy
tidy_prop_test <- broom::tidy(prop_test_result)

# Pull the estimate and confidence intervals
tidy_estimate_ci <- tidy_prop_test %>%
  select(estimate, conf.low, conf.high) %>%
  pull()
```

```{r}

# Create a summary dataframe with counts of unsolved and total homicides by city
city_summary <- homicide_df %>%
  group_by(city, state) %>%
  summarise(
    unsolved_homicides = sum(disposition %in% c("Closed without arrest", "Open/No arrest")),
    total_homicides = n(),
    .groups = "drop"
  )

# Use purrr to apply prop.test to each city and tidy the results
tidy_prop_test_results <- city_summary %>%
  mutate(
    prop_test = map2(unsolved_homicides, total_homicides, ~prop.test(.x, .y)),
    tidy_results = map(prop_test, broom::tidy)
  ) %>%
  select(city, state, tidy_results) %>%
  unnest(tidy_results)
tidy_proportions_ci <- tidy_prop_test_results %>%
  select(city, state, estimate, conf.low, conf.high)
tidy_proportions_ci
```

```{r}
tidy_proportions_ci <- tidy_proportions_ci %>%
  arrange(desc(estimate))
plot <- ggplot(tidy_proportions_ci, aes(x = reorder(city, estimate), y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  coord_flip() +  # Flip the axes to make the plot horizontal
  labs(x = "City", y = "Proportion of Unsolved Homicides", title = "Proportion of Unsolved Homicides by City") +
  theme_minimal()

ggsave(filename = "unsolved_homicides_by_city.png", plot = plot, width = 10, height = 8, dpi = 300)
```

## Problem 2

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

Start with a dataframe containing all file names; the list.files function will help
Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}
# Get the list of file names
file_names <- list.files(path = "./data", pattern = "*.csv")
file_names
# write a function to extract subject id, and arm from the file names
extract_info <- function(filename) {
  subject_id <- str_extract(filename, "\\d+")
  arm <- if_else(str_detect(filename, "^con"), "control", "experimental")
  return(tibble(subject_id = subject_id, arm = arm))
}
info_list <- map(file_names, extract_info)
subject_info <- bind_rows(info_list)
# Print the resulting data frame
print(subject_info)
```



```{r}
# write a function to read observations
read_obs <- function(file_path) {
  df <- read_csv(file_path, show_col_types = FALSE)
  observations_list <- as.list(df[,1])
  observations_list <- lapply(observations_list, as.numeric)
  return(observations_list)
}
 
# use map to read multiple files
file_paths <- list.files(path = "./data", pattern = "*.csv", full.names = TRUE)
data=read_csv(file_paths)
combine=bind_cols(subject_info, data)
combine_long <- combine %>%
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "observations_over_time"
  )
  combine_long
```
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.


```{r}
plot1<-ggplot(combine_long, aes(x = week, y = observations_over_time, group = subject_id, color = arm)) +
  geom_line() +  # draw lines for each subject
  geom_point() +  # add points for observations
  theme_minimal() +  
  facet_grid(. ~ arm) +
  labs(title = "Observations Over Time by Group",
       x = "Week",
       y = "Observations") 
plot1
ggsave("observations_over_time_by_group.png", plot1, width = 10, height = 6, dpi = 300)
```

Based on the graph, the experimental group has higher values of observations over time than that of the control group. The experimental group seems to start with lower observation values compared to the control group but increases steadily over time.The control group’s observations fluctuate around a certain range without a clear trend of increase or decrease over the eight weeks; in contrast, experimental group's observations increase as time progresses.


# Problem 3
write a function to get the outputs of t test
```{r}
set.seed(1234)

sim <- function(n = 30, mu, sigma = 5){
  x = rnorm(n, mean = mu, sd = sigma)
  test <- t.test(x = x, alternative = "two.sided", conf.level = 0.95) |>
    broom::tidy() |>
    select(estimate, p.value)
}
```

let mu=0 and generate 5000 datasets from the model
```{r}
sim_mu_0 <- map_df(1:5000, ~sim(mu = 0))|>
  bind_rows()
```

generate 5000 datasets from the model for mu=1,2,3,4,5,6

```{r}
sim_mu<- 
  tibble(
    mu = c(0, 1, 2, 3, 4, 5, 6)
  ) |>
  mutate(
    estimates = map(.x = mu, ~ map_df(1:5000, ~ sim(30, mu = .x)))
  ) |>
  unnest(estimates)
```

